The imprint of global magma oceans on exoplanet demographics

### 2023-03-14 src/tex/ms.tex
mention HWO, LIFE

With this updated distribution function, planets are generated as in the original \bioverse\ paper, but with an additional stellar mass dependence (for a star of a given mass, the relevant model parameters from the bin containing that mass are used). In summary, stars are assigned a number of planets in accordance with $F_0$, with planet parameters randomly drawn in proportion to the occurrence distribution function evaluated over a grid of radii and orbital periods.
% \todo[inline]{GALEN: Briefly describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions.}
\todo[inline]{GALEN: The most relevant assumption of using our model is that, at the relevant fluxes (I think), we predict that super-Earths are pretty common. I think the "drop" in our model where super-Earths become less common happens at later fluxes than what is relevant in this paper... Let's double check this, and add a note in the first paragraph about it?.}

@@

    Another false positive contribution may come from potential unknown variations in the occurrence rate gradients in radius-instellation space.
    They can impact the statistical inference of the transitions, especially if these variations are similar to the expected pattern.
    Although an abrupt pattern at the expected runaway greenhouse transition seems unlikely, examples of steep occurrence rate density changes exist.
    An example is the "Neptune desert``, a triangular region of low planet occurrence density of close-in planets in period-radius space~\citep{Szabo2011,Mazeh2016,Dreizler2020b}.
    The shape of this region is such that smaller planets become less frequent the closer to the star they are, which to some degree resembles the pattern introduced by the instellation dependency of the runaway greenhouse transition.
    However, the Neptune desert occurs at smaller orbital periods and its location depends on a planet's size~\citep{Szabo2011}, which is not expected for the runaway greenhouse transition.
    \todo{is there overlap/confusion with the radius/density trend in \citet{Luque2022}?}
\end{note}

@@

Similarly, the \tess\ planet sample lacks temperate, small planets around bright host stars~\citep{Ment2023}, as was expected from planet yield calculations~\citep{Barclay2018}.

@@

As \cheops, \ariel~\citep{Puig2016} will be a follow-up mission that is not designed to provide a large number of new radius measurements.
\ariel's primary targets are larger planets in the range of sub-Neptune to Jupiter-like planets.
We thus do not expect a significant contribution to exploring the inner edge of the habitable zone for Earth-sized planets.

@@

>>>>

With this updated distribution function, planets are generated as in the original \bioverse\ paper, but with an additional stellar mass dependence (for a star of a given mass, the relevant model parameters from the bin containing that mass are used). In summary, stars are assigned a number of planets in accordance with $F_0$, with planet parameters randomly drawn in proportion to the occurrence distribution function evaluated over a grid of radii and orbital periods.
\todo[inline]{GALEN: The most relevant assumption of using our model is that, at the relevant fluxes (I think), we predict that super-Earths are pretty common. I think the "drop" in our model where super-Earths become less common happens at later fluxes than what is relevant in this paper... Let's double check this, and add a note in the first paragraph about it?.}

@@

    Another false positive contribution may come from potential unknown variations in the occurrence rate gradients in radius-instellation space.
    They can impact the statistical inference of the transitions, especially if these variations are similar to the expected pattern.
    Although an abrupt pattern at the expected runaway greenhouse transition seems unlikely, examples of steep occurrence rate density changes exist.
    An example is the ``Neptune desert'', a triangular region of low planet occurrence density of close-in planets in period-radius space~\citep{Szabo2011,Mazeh2016,Dreizler2020b}.
    The shape of this region is such that smaller planets become less frequent the closer to the star they are, which to some degree resembles the pattern introduced by the instellation dependency of the runaway greenhouse transition.
    However, the Neptune desert occurs at smaller orbital periods and its location depends on a planet's size~\citep{Szabo2011}, which is not expected for the runaway greenhouse transition.
    \todo{is there overlap/confusion with the radius/density trend in \citet{Luque2022}?}
\end{note}

@@

Similarly, the Transiting Exoplanet Survey Satellite~\citep[\tess,][]{Ricker2014a} planet sample lacks temperate, small planets around bright host stars~\citep{Ment2023}, as was expected from planet yield calculations~\citep{Barclay2018}.

@@

As \cheops, the Atmospheric Remote sensing Infrared Exoplanet Large survey~\citep[\ariel,][]{Puig2016} will be a follow-up mission that is not designed to provide a large number of new radius measurements.
\ariel's primary targets are larger planets in the range of sub-Neptune to Jupiter-like planets.
We thus do not expect a significant contribution to exploring the inner edge of the habitable zone for Earth-sized planets.

@@

Other mission concepts exist that focus on characterizing exoplanet habitability, most notably the \hwo~\citep{Gaudi2020c,LUVOIR2019} and the Large Interferometer For Exoplanets~\citep[\life,][]{Quanz2021}.
Such direct imaging surveys, however, do not directly measure planetary radii and are therefore most useful for providing context through atmospheric measurements of individual planets. \todo[inline]{TIM: feel free to add something about LIFE if you see fit}
